%------------------------- % Resume in Latex % Author : Jake 
Gutierrez % Based off of: https://github.com/sb2nov/resume % 
License : MIT %------------------------ 
\documentclass[letterpaper,11pt]{article} 
\usepackage{latexsym} \usepackage[empty]{fullpage} 
\usepackage{titlesec} \usepackage{marvosym} 
\usepackage[usenames,dvipsnames]{color} \usepackage{verbatim} 
\usepackage{enumitem} \usepackage[hidelinks]{hyperref} 
\usepackage{fancyhdr} \usepackage[english]{babel} 
\usepackage{tabularx} \input{glyphtounicode} %----------FONT 
OPTIONS---------- % sans-serif % 
\usepackage[sfdefault]{FiraSans} % 
\usepackage[sfdefault]{roboto} % 
\usepackage[sfdefault]{noto-sans} % 
\usepackage[default]{sourcesanspro} % serif % 
\usepackage{CormorantGaramond} % \usepackage{charter} 
\pagestyle{fancy} \fancyhf{} % clear all header and footer 
fields \fancyfoot{} \renewcommand{\headrulewidth}{0pt} 
\renewcommand{\footrulewidth}{0pt} % Adjust margins % 
\addtolength{\oddsidemargin}{-0.5in} % 
\addtolength{\evensidemargin}{-0.5in} % 
\addtolength{\textwidth}{1in} % 
\addtolength{\topmargin}{-.5in} % 
\addtolength{\textheight}{1.0in} % Adjust margins 
\usepackage[textheight=700px, margin=0.75in]{geometry} % 
Saving trees ;-) \urlstyle{same} \raggedbottom \raggedright 
\setlength{\tabcolsep}{0in} % Sections formatting 
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% Ensure that generate pdf is machine readable/ATS parsable 
\pdfgentounicode=1 %------------------------- % Custom 
commands \newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}} 
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$} 
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, 
label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}} 
\newcommand{\resumeItemListStart}{\begin{itemize}} 
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}} 
%------------------------------------------- %%%%%% RESUME 
STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%% \begin{document} 
%----------HEADING---------- % 
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r} % 
\textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh 
Bajaj}} & Email : 
\href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\ 
% 
\href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} 
& Mobile : +1-123-456-7890 \\ % \end{tabular*} \begin{center}
    \textbf{\Huge \scshape Connor Luckett} \\ \vspace{1pt}
    98 Elton St. Providence, RI 02906 $|$
    \small (903) 821-4380 $|$
    \href{mailto:cobelu@brown.edu}{\underline{cobelu@brown.edu}} 
$|$
    \href{https://cobelu.com/}{\underline{cobelu.com}} $|$
    % 
\href{https://github.com/cobelu}{\underline{github.com/cobelu}} 
$|$
    
\href{https://www.linkedin.com/in/cobelu/}{\underline{linkedin.com/in/cobelu}} 
\end{center} %-----------EDUCATION----------- 
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Brown University}{Aug. 2019 -- May 2021}
      {Sc.M. of Computer Science (3.92)}{Providence, RI}
    \resumeSubheading
      {Austin College}{Aug. 2015 -- May 2019}
      {B.A. (3.99) of Computer Science (4.0) and Mathematics 
(4.0), Minor in Physics}{Sherman, TX}
    % \resumeSubheading
    % {Sherman High School}{Aug. 2015 -- May 2019}
    % {High School Diploma (4.0)}{Sherman, TX}
  \resumeSubHeadingListEnd %-----------EXPERIENCE----------- 
\section{Experience}
  \resumeSubHeadingListStart
  
      \resumeSubheading
      {Graduate Teaching Assistant}{Jul. 2021 -- Present}
      {Brown University}{Providence, RI}
      \resumeItemListStart
        \resumeItem{Led the Database Management Systems 
course.}
        \resumeItem{Oversaw a team of 8 teaching assistants 
for an 80-student course.}
        \resumeItem{Lectured seminars to explore modern 
trends in database design and research.}
        \resumeItem{Worked with Head TAs to revitalize 
severely outdated course materials.}
      \resumeItemListEnd
    \resumeSubheading
      {Doctoral Researcher}{May 2019 -- Present}
      {Brown University}{Providence, RI}
      \resumeItemListStart
        \resumeItem{Developed a novel tool to help adapt 
legacy systems for GDPR compliance (ICDE ‘21).}
        \resumeItem{Investigated practicality of big-data 
applications on wimpy clusters (ICDE ‘21).}
        \resumeItem{Created a framework to easily compare 
algorithms for matrix factorization in recommendation 
systems.}
      \resumeItemListEnd
    \resumeSubheading
      {Undergraduate Researcher}{June 2018 -- Aug. 2018}
      {University of Rochester}{Rochester, NY}
      \resumeItemListStart
        \resumeItem{Analyzed road paths from OpenStreetMap 
data across a selection of U.S. cities.}
        \resumeItem{Presented results in a public speech and 
poster session.}
        \resumeItem{Engaged with local high-risk youth to 
encourage STEM participation.}
      \resumeItemListEnd
    \resumeSubheading
      {Student Team Leader}{Jan. 2018 -- May 2018}
      {Austin College}{Sherman, TX}
      \resumeItemListStart
        \resumeItem{Oversaw a students team in assisting 
Meals On Wheels of Tarrant County.}
        \resumeItem{Prototyped an iPad application to assist 
organization of roughly 6,000 clients.}
        \resumeItem{Gathered location data using Google Maps 
APIs.}
      \resumeItemListEnd
      
    \resumeSubheading
       {Mathematics Tutor}{Sept. 2017 -- Dec. 2017}
       {Austin College}{Sherman, TX}
       \resumeItemListStart
         \resumeItem{Provided weekly one-to-one instruction 
in middle and high school mathematics.}
         \resumeItem{Funded by a National Science Foundation 
Noyce Grant.}
       \resumeItemListEnd
      
    \resumeSubheading
      {Seasonal Teller}{June 2015 -- Jan. 2018}
      {Independent Financial}{Sherman, TX}
      \resumeItemListStart
        \resumeItem{Provided account services at the 
corporation’s most active branch.}
        \resumeItem{Received training in Bank Secrecy Act and 
OFAC.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd % %-----------PROJECTS----------- 
% \section{Projects} % \resumeSubHeadingListStart % 
\resumeProjectHeading % 
{\textbf{\href{https://github.com/cobelu/PyWander}{\underline{Wander}}} 
$|$ \emph{Python, Ray}}{Fall 2020 -- Present} % 
\resumeItemListStart % \resumeItem{Developing a unified 
framework for distributed stochastic gradient descent.} % 
\resumeItem{Evaluating performance of various partitioning 
and scheduling algorithms in a fairer manner.} % 
\resumeItemListEnd % \resumeProjectHeading % 
{\textbf{\href{https://github.com/cobelu/odlaw}{\underline{Odlaw}} 
$|$ % } $|$ \emph{Python, NetworkX, pandas, SQLAlchemy}}{Fall 
2019} % \resumeItemListStart % \resumeItem{Developed a 
command line application to assist with retroactive GDPR 
compliance.} % \resumeItem{Allowed bolt-on functionality for 
access, portability, and erasure in relational back-ends.} % 
\resumeItem{Wrote database connectors to PostgreSQL, MySQL, 
and SQLite.} % \resumeItem{Presented demonstration to 
Privacy-Conscious Computer Systems course.} % 
\resumeItem{Repackaged with a front-end and accepted as a 
demo for ICDE 2021.} % \resumeItemListEnd % 
\resumeSubHeadingListEnd % %-----------PROGRAMMING 
SKILLS----------- \section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Courses}{: Artificial Intelligence, Data 
Science, Database Systems, Design and Analysis of Algorithms, 
Distributed Systems, Microservices (current) 
Privacy-Conscious Systems, Probability Theory} \\
     \textbf{Languages}{: C, Go, Java, Python, R, Scala, SQL, 
Swift} \\
     \textbf{Libraries}{: gRPC, pandas, Matplotlib, NumPy, 
Spark, SQLAlchemy} \\
     \textbf{Interests}{: CAM, Composites, Homebuilt 
Aircraft, Lathe, Mill, Private Pilot, 3D Printing}
 }}
 \end{itemize} %-------------------------------------------
\end{document}
